A user-extensible and adaptable parser architecture

### 2008-06-02 papers/sgai-2008/paper.tex
Explained priority in a bit more detail.

    \item [priority] This is the user-configurable companion to hits:
        priority overrides hits when sorting rules, allowing more
        specific rules to take precedence over more general rules.

>>>>

    \item [priority] Priority overrides hits when sorting rules, allowing
        more specific rules to take precedence over more general rules.  To
        illustrate: most warnings are ignored by a rule whose regex matches
        \verb!^warning:.*$!, but some warnings require a different action
        to be taken, e.g.\ when a client tries to send a mail larger than
        the maximum size the server accepts, the data structure for that
        mail must be discarded because it won't have all the data required
        to save it to the database.
